Implementation and verification of a data structure using dependent types

### 2022-04-30 paper/main.tex
Fix OCaml syntax highlighting

\begin{coq}
Extract Inductive array => "array" [ "(assert false)" ] "(assert false)".
Extract Constant array_to_list => "fun _ a -> Array.to_list a".
Extract Inlined Constant array_empty => "[||]".
Extract Constant array_single => "fun x -> [|x|]".
Extract Constant array_nth => "
  fun _ i a ->
    try Some a.(i)
    with Invalid_argument _ -> None
".
Extract Constant array_update => "
  fun _ i x a ->
    let a0 = Array.copy a in
    try
      a0.(i) <- x;
      Some a0
    with Invalid_argument _ -> None
".
Extract Constant array_push => "
  fun n x a ->
    let a0 = Array.make (n + 1) x in
    Array.blit a 0 a0 0 n;
    a0
".
Extract Constant array_pop => "fun n a -> (Array.sub a 0 n, a.(n))".
\end{coq}

@@

@@

  let main =
    time (lazy (
      let r = 32 in
      let cdl = concrete_digital_list_empty r |> ref in
      for _ = 0 to 10000000 do
        cdl := !cdl |> concrete_digital_list_push r 0
      done;
      for i = 0 to (!cdl |> concrete_digital_list_length r) - 1 do
        cdl := !cdl |> concrete_digital_list_update r i (i mod 123) |> Option.get
      done;
      let a = Array.make (!cdl |> concrete_digital_list_length r) 0 in
      for i = 0 to (!cdl |> concrete_digital_list_length r) - 1 do
        a.(i) <- !cdl |> concrete_digital_list_nth r i |> Option.get
      done;
      Printf.printf "Raw data size (after serialization): %f MiB\n" ((Marshal.to_bytes a [] |> Bytes.length |> float_of_int) /. 1024.0 /. 1024.0);
      Printf.printf "Data structure size (after serialization): %f MiB\n" ((Marshal.to_bytes !cdl [] |> Bytes.length |> float_of_int) /. 1024.0 /. 1024.0)
    ))
end

>>>>

\begin{coq}
Extract Inductive array => ``array'' [ ``(assert false)'' ] ``(assert false)''.
Extract Constant array_to_list => ``fun _ a -> Array.to_list a''.
Extract Inlined Constant array_empty => ``[||]''.
Extract Constant array_single => ``fun x -> [|x|]''.
Extract Constant array_nth => ``
  fun _ i a ->
    try Some a.(i)
    with Invalid_argument _ -> None
''.
Extract Constant array_update => ``
  fun _ i x a ->
    let a0 = Array.copy a in
    try
      a0.(i) <- x;
      Some a0
    with Invalid_argument _ -> None
''.
Extract Constant array_push => ``
  fun n x a ->
    let a0 = Array.make (n + 1) x in
    Array.blit a 0 a0 0 n;
    a0
''.
Extract Constant array_pop => ``fun n a -> (Array.sub a 0 n, a.(n))''.
\end{coq}

@@

let measure_size x = (Marshal.to_bytes x [] |> Bytes.length |> float_of_int) /. 1024.0 /. 1024.0

@@

  let main =
    time (lazy (
      let r = 32 in
      let cdl = concrete_digital_list_empty r |> ref in
      for _ = 0 to 10000000 do
        cdl := !cdl |> concrete_digital_list_push r 0
      done;
      for i = 0 to (!cdl |> concrete_digital_list_length r) - 1 do
        cdl := !cdl |> concrete_digital_list_update r i (i mod 123) |> Option.get
      done;
      let a = Array.make (!cdl |> concrete_digital_list_length r) 0 in
      for i = 0 to (!cdl |> concrete_digital_list_length r) - 1 do
        a.(i) <- !cdl |> concrete_digital_list_nth r i |> Option.get
      done;
      Printf.printf "Raw data size (after serialization): %f MiB\n" (a |> measure_size);
      Printf.printf "Data structure size (after serialization): %f MiB\n" (cdl |> measure_size)
    ))
end
